### 2021-07-12 src/paper/model/number_of_contacts.tex
Remove comment.

types of contacts:\comment[id=HM]{I started updating this to understand it better myself.
In the end, I think it will be useful to group into HH / work / schools and add an
introductory sentence for each group. E.g., that work is for everybody who is working ---
except there is a different model for teachers (?), ...}

>>>>

types of contacts:
